Are iPhone users more secure when using mobile enterprise systems?

### 2021-04-16 outputs/paper/paper.Rmd
update

```{r echo=FALSE}
####read the clean data 
library(here) # locate the file path
clean_data<- read.csv(here::here("inputs/DATA/clean_data.csv"))
```

## T-test
## correlation model
## propensity score matching
## regression model

>>>>

```{r ,echo=FALSE}
####read the clean data 
library(here) # locate the file path
clean_data<- read.csv(here::here("inputs/DATA/clean_data.csv"))
```

## Difference in means: outcome variable

## T-test
We can carry out t-tests to evaluate whether these means are statistically distinguishable:

## correlation model

## propensity score matching

## regression model
